disaggregation: An \proglang{R} package for Bayesian spatial disaggregation modelling

### 2019-11-21 article.Rnw
Try that sentence again.

Methods for estimating high-resolution risk maps from aggregated response data over large spatial regions are 
becoming increasingly sought after in disease risk mapping~\cite{li2012log, diggle2013spatial, wilson2017pointless}, especially in malaria mapping~\cite{sturrock2014fine, sturrock2016mapping}. 
Disaggregation regression, was first applied to ecological species distribution modelling~\cite{keil2013downscaling, barwell2014can} but has now become an important method in disease risk mapping \cite{falciparum2019, vivax2019}. 
The aggregation of response data over large heterogenous regions is problematic for understanding the fine-scale distribution. However, by using fine-scale information from related covariates we can inform the hetrogeneity of the response variable of interest within the agreggated area.

>>>>

Methods for estimating high-resolution risk maps from aggregated response data over large spatial regions are 
becoming increasingly sought after in disease risk mapping~\cite{li2012log, diggle2013spatial, wilson2017pointless}, especially in malaria mapping~\cite{sturrock2014fine, sturrock2016mapping}. 
Disaggregation regression, first applied in species distribution modelling in ecology~\cite{keil2013downscaling, barwell2014can} has now become an important method in disease risk mapping \cite{falciparum2019, vivax2019}. 
The aggregation of response data over large heterogenous regions is problematic for understanding the fine-scale distribution. However, by using fine-scale information from related covariates we can inform the hetrogeneity of the response variable of interest within the agreggated area.
